\documentclass[12pt]{article}
\usepackage[a4paper, margin=2.5cm]{geometry}
\usepackage{lmodern}
\usepackage{hyperref}
\usepackage{longtable}
\usepackage{titlesec}
\titleformat{\section}{\normalfont\large\bfseries}{\thesection}{1em}{}
%nina note: strg,alt,b to build

\title{Project Proposal\\\large infrared.city-1: Tree detection}
\author{
Moritz Hörmansdorfer (h) \\
Sara Klasová (h12122714) \\
Dominik Oberhumer (h01025454) \\
Nina Salnikow (h12109432) \\
}
\date{\today}

\begin{document}

\maketitle

\section{Project Description}

TODO A refined descriptionand definition of the now agreed upon project. Particularly explain what isin scopeand also what isout of scopeof your planned work.

\section{BEAM}

TODO a BEAM figure

\section{Timeplan}

TODO set of Milestones and Tasks, including deliverables

\section{Communication outline}

This section describes the communication stiles we are commited to use over the project.

\subsection{Written communication}

We will use two Teams in Microsoft Teams for our basic communication.

1. \textbf{DsLab26S\_infrared.city\_1}: This Team contains two channels for two different approaches. The \textbf{General} Channel is used as communication level with Kavita Surana (our connection to the Lecture and the WU). The other channel (\textbf{team intern}) is only accessable by the team itself and is our main chat for communication over the project.

2. \textbf{DsLab\_infrared.city\_1-coaches}: This Team is the basic for communication with the data coaches from infrared-city. We were asked to separate this from the main communication source, but still keep an Microsoft Team Teams for this. So we created an different Team

\subsection{Regular Meetings}

Our Meetings will be hold via Microsoft Teams in most cases. Possible that we are able to meet in person for the one or other defined meeting. But regulary we plan to keep the communication remote or at least hibrate.

We organized already two regulary weekly meetings for basic communication.

1. \textbf{Regular Team Meeting}: On Thursdays 19:00 we will meet as a team remote and talk about how to continue the work over the next week.

2. \textbf{Meeting with Data Coaches from infrared.city} On Fridays 12:30 we scheduled a short regulary meeting with the data coaches from infrared.city.

3. \textbf{Irregular Meetings with Kavita Surana}: In cases we need feedback for something from the WU site we schedule a meeting with her. To easily schedule the meeting we got an booking site for her time.

\subsection{Documentation of Meetings}

Because of the many meetings it is possible that the one or other person is not able to partizipate every time. To still be able to communicate with absent people we want to write meeting notes and documentation of the meeting output after every meeting.

\subsection{GIT}

Every written result (documenation and project related) will be added to an already created GitHub repository. The repository is accessable by the team. See \url{https://github.com/nikmaster/wu_dslab_infrared-city}


\section{Team Roles}

\begin{tabular}{|l|l|}
\hline
\textbf{Person} & \textbf{Role} \\
\hline
Dominik & Organisation of Team \\
Moritz & TODO \\
Nina & Data Engineer (so, initial EDA for cleaning, and preparing the data)  \\
Sara & TODO  \\
\hline
\end{tabular}

TODO roles: Data Engineer? Data Scientist? Visualization der daten? Development (projekt)? ethics? ui/ux? tester?

\section{Literature}

TODO list of liturate

\end{document}
