\section{Related Work}

The detection and classification of urban trees using remote sensing imagery is a rapidly evolving field, characterized by a transition from traditional algorithms to advanced machine learning techniques. A comprehensive overview is provided by Zheng et al. \cite{zheng2023reviewindividualtreecrown}, who review various methods for individual tree crown detection and delineation from optical imagery, highlighting the growing reliance on deep learning architectures. Building on this methodological shift, Durgut et al. \cite{durgut2025integrating} demonstrate the benefits of integrating traditional image processing methods with modern deep learning approaches to further enhance the accuracy of tree crown detection in satellite images. \\
\\
A significant portion of recent research focuses on highly detailed classification tasks utilizing very high-resolution (VHR) imagery. For instance, Sicard et al. \cite{sicard2023object} explore object-based classification techniques to accurately distinguish different urban plant species. Similarly, Wenger et al. \cite{wenger2024improving} focus on improving urban tree species classification by combining VHR satellite data with various machine learning models. While these approaches achieve high precision at the individual tree level, they often depend on commercial or less frequently updated satellite data, which can limit the scalability and temporal analysis required for continuous urban climate monitoring.\\\
\\
Addressing the need for scalable and frequently updated data, recent studies have increasingly adopted Sentinel-2 imagery for forestry and urban green space applications. Notably, Freudenberg et al. \cite{freudenberg2025sentinel2} introduce a dedicated Sentinel-2 machine learning dataset specifically designed for tree species classification in Germany. Their work underscores the viability of using freely available, multi-spectral satellite data for large-scale vegetation mapping. \\
\\
Furthermore, recent advancements highlight the critical role of multi-temporal analysis in vegetation mapping. Because the spectral signature of trees changes significantly throughout the year due to phänological cycles, relying on single-date imagery often leads to misclassifications. Grabska et al. \cite{grabska2019forest} demonstrate that incorporating the entire Sentinel-2 time series—capturing leaf-on, leaf-off, and flowering periods—greatly enhances the ability of models to differentiate vegetation types. Integrating these temporal signals into deep learning architectures, such as through convolutional temporal attention networks, allows models to prioritize the most meaningful seasonal features for precise identification \cite{garnot2021panoptic, grabska2019forest}. \\
\\
Overall, while existing literature predominantly focuses either on VHR imagery for exact crown delineation or on traditional models for general species classification, our project bridges these areas. By leveraging the temporal resolution of Sentinel-2 data \cite{freudenberg2025sentinel2, grabska2019forest} combined with a temporal attention U-Net architecture \cite{garnot2021panoptic}, this study aims to provide a scalable and robust solution for urban tree detection that does not rely on costly VHR imagery.